Accuracy and precision of zero-heat-flux temperature monitoring: a systematic review and meta- analysis

### 2019-09-23 zhf_manuscript/zhf_manuscript.Rmd
new author

authors: 
- name: Aaron Conway
  address: Peter Munk Cardiac Centre, UHN & Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
  email: aaron.conway@utoronto.ca

>>>>

authors: 
- name: Aaron Conway
  address: Peter Munk Cardiac Centre, UHN & Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
  email: aaron.conway@utoronto.ca
- name: Navpreet Kamboj
  address: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
  email: navpreet.kamboj@mail.utoronto.ca
